\section*{ACKNOWLEDGEMENTS}
I would like to thank Glide for collaborating with Curtin University on this thesis project
and providing a powered wheelchair to the research team.

Further thanks go to Siavash Khaksar and Yifei Ren,
for supervising this thesis and providing invaluable technical knowledge and support.

I am also grateful to the remaining smart wheelchair thesis project students;
collaborating with likeminded engineers to research a semi-autonomous smart
wheelchair was a highlight of this engineering thesis.

% TODO include other acknowledgements
\cleardoublepage

\section*{ABSTRACT}
Semi-autonomous smart wheelchair technology can enable visually impaired users to drive a wheelchair
safely. In collaboration with wheelchair manufacturer Glide, a navigation assistance system for a
smart wheelchair is implemented and evaluated. This smart wheelchair uses a CentroGlide wheelchair
as a powered base and a ZED Mini RGB-D stereo camera to detect the surrounding environment.
A semantic segmentation ML model was retrained to identify footpaths and other drivable areas around the wheelchair.
Additionally, an algorithm was developed to identify obstacles and hazards using 3D point cloud data from the stereo camera.
A birds-eye view occupancy map is generated to indicate the location of obstacles and drivable areas
around the wheelchair. This occupancy map is used to determine a safe target direction for the wheelchair.
To evaluate this navigation assistance system, an RGB-D wheelchair driving dataset was collected
around Curtin University. It was found that the identification of drivable areas using semantic segmentation was effective in outdoor
areas but less effective indoors. Obstacle detection was effective at identifying environmental obstacles such as
walls and handrails. The assistive control algorithm successfully modifies the wheelchair's direction to avoid obstacles,
however, can fail in some scenarios due to the low FOV of the stereo camera. Suggestions for future work are also discussed.
\cleardoublepage

\section*{DECLARATION OF PUBLISHED WORKS}
% TODO use format provided by Siavash
I acknowledge that the literature review of this thesis was previously submitted as part of the Progress Report assessment for MXEN4000.
Additionally, I acknowledge that parts of the `Evaluation of ML models on preliminary dataset'
section of the methodology was previously submitted as part of the same progress report assessment.
I also acknowledge that this thesis contains no material previously
published by any other person except where due acknowledgment has been made.
